---
title: "R Notebook"
output: html_notebook
---

- Execute chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 


- Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
- When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
- The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
R


```{r}
vec <- c(1, 2, 3)
vec 
```

```{r}

# install.packages("ggplot2")

library(ggplot2)

```


# Vektor

Programovací jazyk R podporuje několik různých datových typů/struktur z nichž však lze vektor považovat za základní. Jde o datovou strukturu (kontejner) uchovávájící skupinu hodnonot.  Vektor je v R *homogenní datová struktura* to znamená, že v něm uložené hodnoty jsou jednoho datového typu. 

```{r}



```


# Seznam